CASTRO: A New Compressible Astrophysical Solver. IV. Performance Portability and GPUs

### 2019-05-15 gpus/paper.tex
some tweaks
add note
Frame not-Kokkos positively, not negatively

@@

In this paper, we describe our approach to performance portability
with the \castro\ multiphysics simulation code.  We choose not to use
a framework like Kokkos but instead we implement the mechanism for
offloading compute kernels to GPUs inside of the AMReX adaptive mesh
refinement library itself.  Our goal is to have the same computational
kernels run efficiently on CPUs (including manycore processors) and
GPUs.  Early GPU results with a version of \castro\ were described in
\citet{astronum:2017}.  Here, we describe the work we needed to do to
enable this portability and show performance metrics for a reacting
flow problem in astrophysics.

@@

>>>>

\received{XXX X, XXXX}
\revised{XXX X, XXXX}
\accepted{XXX X, XXXX}
%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{ApJ}

@@

In this paper, we describe our approach to performance portability
with the \castro\ multiphysics simulation code.  Similar to the approaches
of Kokkos and RAJA, we have implemented a mechanism for offloading compute
kernels to GPUs inside of the AMReX adaptive mesh refinement library.
Our goal is to have the same computational
kernels run efficiently on CPUs (including manycore processors) and
GPUs.  Early GPU results with a version of \castro\ were described in
\citet{astronum:2017}.  Here, we describe the work we needed to do to
enable this portability and show performance metrics for a reacting
flow problem in astrophysics.

@@

needed to change to variable sizes known at compile time
